MSF_Groupwork-NBA_shotlog

### 2016-10-13 MSFGroupwork-NBAHotHand.Rmd
added df for accuracy in general and df per player(not finished)

```{r}
# replacing W/L in column "W" with 1/0 (1 for win, 0 for loss)
df[,"W"] <- as.character(df[,"W"])

@@

restdays<-cast(df1, DATE+ HOME_TEAM + AWAY_TEAM + WINNER ~ FGM)

for i in aa3$TEAM {
  for (j in 1:nrow(restdays)) {aa3$DATES<- as.list(aa3$DATES)
    if (restdays$HOME_TEAM[j]=="LAL" ) aa3$DATES[aa3$TEAM=="LAL"]<- c(aa3$DATES[aa3$TEAM=="LAL"], restdays$DATE[j])}
}

#| restdays$AWAY_TEAM[j])=="LAL"

@@

df[, "OVERTIME"] <- as.numeric()

for (i in 1:nrow(df)) {
  if (df[i, "PERIOD"] >= 5) df[i, "OVERTIME"] <- 1
  if (df[i, "PERIOD"] <= 4) df[i, "OVERTIME"] <- 0
}

# accuracy 
acc_ot <- as.numeric
acc_ot <- sum(df$OVERTIME == 1 & df$FGM == 1)/sum(df$OVERTIME == 1)

acc_qrt1 <- as.numeric
acc_qrt1 <- sum(df$PERIOD == 1 & df$FGM == 1)/sum(df$PERIOD == 1)

acc_qrt2 <- as.numeric
acc_qrt2 <- sum(df$PERIOD == 2 & df$FGM == 1)/sum(df$PERIOD == 2)

acc_qrt3 <- as.numeric
acc_qrt3 <- sum(df$PERIOD == 3 & df$FGM == 1)/sum(df$PERIOD == 3)

acc_qrt4 <- as.numeric
acc_qrt4 <- sum(df$PERIOD == 4 & df$FGM == 1)/sum(df$PERIOD == 4)

acc_qrt5 <- as.numeric
acc_qrt5 <- sum(df$PERIOD == 5 & df$FGM == 1)/sum(df$PERIOD == 5)

acc_qrt6 <- as.numeric
acc_qrt6 <- sum(df$PERIOD == 6 & df$FGM == 1)/sum(df$PERIOD == 6)

acc_qrt7 <- as.numeric
acc_qrt7 <- sum(df$PERIOD == 7 & df$FGM == 1)/sum(df$PERIOD == 7)

acc_qrt1_4 <- as.numeric
acc_qrt1_4 <- sum(df$PERIOD <= 4 & df$FGM == 1) / sum(df$PERIOD <= 4)

t.test(df$FGM[df$PERIOD <= 4], df$FGM[df$PERIOD >= 5])
t.test(df$FGM[df$PERIOD == 1], df$FGM[df$PERIOD == 2])
t.test(df$FGM[df$PERIOD == 2], df$FGM[df$PERIOD == 3])
t.test(df$FGM[df$PERIOD == 3], df$FGM[df$PERIOD == 4])
t.test(df$FGM[df$PERIOD == 1], df$FGM[df$PERIOD == 3])
t.test(df$FGM[df$PERIOD == 2], df$FGM[df$PERIOD == 4])

# accuracy for Top 10 scoring players

@@

acc <- data.frame()

#accuracy for every second
for (i in 1:23){
  acc[i, "Accuracy"] <- (sum(df$SHOT_CLOCK > i & df$SHOT_CLOCK <= i+1 & df$SHOT_CLOCK != 99 & df$FGM == 1)/ sum(df$SHOT_CLOCK > i & df$SHOT_CLOCK <= i+1 & df$SHOT_CLOCK != 99))}

acc[, "SECONDS_LEFT"] <- c(1:23)

ggplot(acc, aes(x = SECONDS_LEFT, y = Accuracy)) + geom_point() + geom_smooth()

df[, "ACC_P_SEC"] <- as.numeric()

#Assign accuracy per second to main dataframe
for (i in 1:nrow(df)){
  for (j in 1:23){
    if (df$SHOT_CLOCK[i] >j & df$SHOT_CLOCK[i] <= j+1 & df$SHOT_CLOCK[i] != 99) df[i, "ACC_P_SEC"] <- acc[j, "Accuracy"]
  }
}

cov(df$ACC_P_SEC, df$SHOT_CLOCK)
cor.test(df$ACC_P_SEC, df$SHOT_CLOCK)

>>>>

# replacing W/L in column "W" with 1/0 (1 for win, 0 for loss)
df[,"W"] <- as.character(df[,"W"])

@@

restdays<-cast(df1, DATE+ HOME_TEAM + AWAY_TEAM + WINNER ~ FGM)
```

@@

df[, "overtime"] <- as.numeric()

for (i in 1:nrow(df)) {
  if (df[i, "PERIOD"] >= 5) df[i, "overtime"] <- 1
  if (df[i, "PERIOD"] <= 4) df[i, "overtime"] <- 0
}

# accuracy

df.acc <- data.frame()

for (i in (1:7)){
  df.acc[i, "accuracy"] <- sum(df$PERIOD == i & df$FGM == 1)/sum(df$PERIOD == i)
  df.acc[i, "period"] <- i
  if (df.acc$period[i] <= 4) df.acc[i, "overtime"] <- 0
  if (df.acc$period[i] >= 5) df.acc[i, "overtime"] <- 1
}

t.test(df$FGM[df$PERIOD == 1], df$FGM[df$PERIOD == 2])
t.test(df$FGM[df$PERIOD == 2], df$FGM[df$PERIOD == 3])
t.test(df$FGM[df$PERIOD == 3], df$FGM[df$PERIOD == 4])
t.test(df$FGM[df$PERIOD == 1], df$FGM[df$PERIOD == 3])
t.test(df$FGM[df$PERIOD == 2], df$FGM[df$PERIOD == 4])

# accuracy per player per period

df.period <- cast(df, player_id + player_name + PERIOD ~ FGM)

df.period[, "accuracy"] <- as.numeric()

for (i in 1:nrow(df.period)){
  df.period[i, "accuracy"] <- df.period[i, "1"] / sum(df.period[i, "1"], df.period[i, "0"] ) }

# do analysis for top players per team in regards of accuracy per period

@@

acc <- data.frame(seconds.left = c(0:23))

#accuracy for every second
for (i in (0:23)){
  acc[i, "accuracy"] <- (sum(df$SHOT_CLOCK >= i & df$SHOT_CLOCK < i+1 & df$SHOT_CLOCK != 99 & df$FGM == 1)/           sum(df$SHOT_CLOCK >= i & df$SHOT_CLOCK < i+1 & df$SHOT_CLOCK != 99))}

ggplot(acc, aes(x = seconds.left, y = accuracy)) + geom_point() + geom_smooth()

#accuracy for players per second

##simplifying shot clock to seconds left

df.acc.players <- cast(df, player_id + player_name + SHOT_CLOCK ~ FGM)

for (i in (1:nrow(df.acc.players))){
  for (j in (0:23)){
    if (df.acc.players$SHOT_CLOCK[i] >= j & df.acc.players$SHOT_CLOCK[i] < j+1) df.acc.players[i, "seconds.left"] <- j
    if (df.acc.players$SHOT_CLOCK[i] == 99) df.acc.players[i, "seconds.left"] <- 99}
}

df.acc.players[, "acc.per.sec"] <- as.numeric()

for (i in (1:nrow(df.acc.players))){
  df.acc.players[i, "acc.per.sec"] <- sum(df.acc.players$'0'[df.acc.players$seconds.left == df.acc.players$seconds.left[i] & df.acc.players$player_id == df.acc.players$players_id[i]])} ### doesnt work as I would like it

ggplot(df.acc.players, aes(x = seconds.left, y = ))

#Assign accuracy per second to main dataframe
df[, "acc.per.sec"] <- as.numeric()

for (i in 1:nrow(df)){
  for (j in 0:23){
    if (df$SHOT_CLOCK[i] >j & df$SHOT_CLOCK[i] <= j+1 & df$SHOT_CLOCK[i] != 99) df[i, "acc.per.sec"] <- acc[j, "accuracy"]
  }
}
